\textsc{\wobble: a data-driven \changed{analysis technique for time-series stellar spectra}}

### 2019-09-17 paper/paper.tex
added zenodo reference

Our code is made open-source under the \acronym{MIT} license and is publicly available on GitHub.\footnote{\url{https://www.github.com/megbedell/wobble}}

>>>>

Our code is made open-source under the \acronym{MIT} license and is publicly available on GitHub.\footnote{\url{https://www.github.com/megbedell/wobble}; in this work, we use the version released as Zenodo v0.1.0 \citep{wobble-code}}
